### 2024-02-09 paper_sisc_first_revision/localpsf.tex
editing figures with noemi

\begin{figure}
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[scale=0.2]{kernel_impulse_illustration2.pdf}
		\caption{Kernel and impulse responses}
		\label{fig:kernel_impulse_illustration}
	\end{subfigure}
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[scale=0.4]{frog_ellipsoid_width2.pdf}
		\caption{Impulse response support ellipsoid}
		\label{fig:frog_ellipsoid_width}
	\end{subfigure}

	\caption{(\ref{fig:kernel_impulse_illustration}) asdf. \ref{fig:frog_ellipsoid_width}) asdf2
	}
	\label{fig:frog1}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[scale=0.2]{frog_moments2.pdf}	
	\caption{asdf3
	}
	\label{fig:frog2}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[scale=0.25]{frog_batches2.pdf}	
	\caption{asdf4
	}
	\label{fig:frog3}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[scale=0.2]{frog_hmatrix_knn_impulse2.png}	
	\caption{asdfg
	}
	\label{fig:frog4}
\end{figure}

\begin{figure}
	\begin{subfigure}[b]{0.30\textwidth}
		\centering
		\includegraphics[scale=0.35]{frog_column_errors_psf5.png}
		\caption{PSF(5)}
		\label{fig:blur_error_psf5}
	\end{subfigure}
	\begin{subfigure}[b]{0.30\textwidth}
		\centering
		\includegraphics[scale=0.35]{frog_column_errors_psf10.png}
		\caption{PSF(10)}
		\label{fig:blur_error_psf10}
	\end{subfigure}
	\begin{subfigure}[b]{0.37\textwidth}
		\centering
		\includegraphics[scale=0.35]{frog_column_errors_psf20_colorbar.png}
		\caption{PSF(20)}
		\label{fig:blur_error_psf20}
	\end{subfigure}

	\caption{columnwise error plots for kernel reconstruction
	}
	\label{fig:frog5}
\end{figure}

>>>>

\begin{figure}
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[scale=0.25]{kernel_impulse_illustration2.pdf}
%		\caption{Kernel and impulse responses}
		\label{fig:kernel_impulse_illustration}
	\end{subfigure}
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[scale=0.5]{frog_ellipsoid_width2.pdf}
%		\caption{Impulse response support ellipsoid}
		\label{fig:frog_ellipsoid_width}
	\end{subfigure}

	\caption{left kernel and impulse responses. right impulse response support ellipsoid
	}
	\label{fig:frog1}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[scale=0.25]{frog_moments2.pdf}	
	\caption{asdf3
	}
	\label{fig:frog2}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[scale=0.3]{frog_batches3.pdf}	
	\caption{asdf4
	}
	\label{fig:frog3}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[scale=0.2]{frog_hmatrix_knn_impulse3.pdf}	
	\caption{asdfg
	}
	\label{fig:frog4}
\end{figure}

\begin{figure}
	\begin{subfigure}[b]{0.30\textwidth}
		\centering
		\includegraphics[scale=0.35]{frog_column_errors_psf5.png}
%		\caption{PSF(5)}
		\label{fig:blur_error_psf5}
	\end{subfigure}
	\begin{subfigure}[b]{0.30\textwidth}
		\centering
		\includegraphics[scale=0.35]{frog_column_errors_psf10.png}
%		\caption{PSF(10)}
		\label{fig:blur_error_psf10}
	\end{subfigure}
	\begin{subfigure}[b]{0.30\textwidth}
		\centering
		\includegraphics[scale=0.35]{frog_column_errors_psf20.png}
%		\caption{PSF(20)}
		\label{fig:blur_error_psf20}
		\end{subfigure}
			\begin{subfigure}[b]{0.08\textwidth}
			\centering
			\includegraphics[scale=0.35]{frog_colorbar_edited1.pdf}
			\label{fig:blur_colorbar}
		\end{subfigure}

	\caption{columnwise error plots for kernel reconstruction left 5, center 10, right 20
	}
	\label{fig:frog5}
\end{figure}
